% ============================================================
% NERCCS 2026 — Remote / Zoom Attendee & Presenter Logistics
% ============================================================

\documentclass[11pt]{article}
\usepackage{kpfonts}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{}
\lhead{NERCCS 2026}
\rhead{Remote / Zoom Logistics}
\cfoot{\thepage}

\titleformat{\section}{\Large\bfseries}{}{0pt}{}[\vspace{-0.3em}\rule{\textwidth}{0.4pt}]
\titleformat{\subsection}{\large\bfseries}{}{0pt}{}

\setlist[itemize]{itemsep=0.3em, topsep=0.3em}

% ============================================================
\begin{document}

\begin{center}
    {\LARGE\bfseries NERCCS 2026 — Remote Participation Logistics}\\[0.5em]
    {\large Ninth Northeast Regional Conference on Complex Systems}\\[0.3em]
    {\normalsize March 11--13, 2026 \quad|\quad Online via Zoom}\\[0.3em]
    {\normalsize All times in U.S. Eastern Daylight Time (EDT = UTC$-$04:00)}\\[0.3em]
    {\normalsize Questions? \href{mailto:nerccs2026@gmail.com}{nerccs2026@gmail.com}}
\end{center}

\vspace{1em}

% ============================================================
\section{Zoom Meeting Links}

There are two simultaneous rooms during parallel sessions.
Check the program book to determine which room your talk or session of interest is in.

\subsection{Room 1 — Sloan Auditorium (Goergen 101)}
\textit{Keynotes and parallel sessions are held here.}\\[0.5em]
\textbf{Zoom Link:} \href{PLACEHOLDER_ZOOM_LINK_AUDITORIUM}{[PLACEHOLDER: Zoom link for Sloan Auditorium]}\\
\textbf{Meeting ID:} [PLACEHOLDER: Meeting ID]\\
\textbf{Passcode:} [PLACEHOLDER: Passcode]

\subsection{Room 2 — Fantone Lecture Hall (Goergen 109)}
\textit{Parallel sessions only; no keynotes in this room.}\\[0.5em]
\textbf{Zoom Link:} \href{PLACEHOLDER_ZOOM_LINK_LECTUREHALL}{[PLACEHOLDER: Zoom link for Fantone Lecture Hall]}\\
\textbf{Meeting ID:} [PLACEHOLDER: Meeting ID]\\
\textbf{Passcode:} [PLACEHOLDER: Passcode]

\vspace{0.5em}
\noindent\textit{Note: Keynotes take place in Room 1 (Sloan Auditorium) only.
During parallel session blocks, remote attendees should join whichever room contains the session they wish to attend.}

% ============================================================
\section{Schedule Overview}

Full schedule with room assignments is in the \textbf{Conference Program Book} (linked from the conference website).\\[0.3em]
\textbf{Conference hours (EDT):}
\begin{itemize}
    \item \textbf{Day 1 — Wednesday, March 11:} 1:00 pm -- 5:00 pm
    \item \textbf{Day 2 — Thursday, March 12:} 9:15 am -- 5:00 pm
    \item \textbf{Day 3 — Friday, March 13:} 9:15 am -- 12:00 pm
\end{itemize}

% ============================================================
\section{For Remote Attendees}

\begin{itemize}
    \item Join the appropriate Zoom room 5--10 minutes before each session.
    \item \textbf{Cameras and microphones are muted by default.} Please keep your microphone muted unless asking a question.
    \item Questions may be submitted via the \textbf{Zoom chat} or the \textbf{Q\&A feature}; a session host will relay questions to the speaker.
    \item Zoom recordings: [PLACEHOLDER: state whether sessions will be recorded and/or shared post-conference.]
\end{itemize}

% ============================================================
\section{For Remote Presenters}

\begin{itemize}
    \item Check the program book for your \textbf{room assignment} and \textbf{talk time (EDT)}.
    \item \textbf{Talk slots are 20 minutes} (15 min talk + 5 min Q\&A).
    \item Join your assigned Zoom room \textbf{at least 10 minutes before your session begins} so the host can promote you to presenter and test your screen share.
    \item You will share your screen directly in Zoom. Test your screen-share before the conference.
    \item Contact \href{mailto:nerccs2026@gmail.com}{nerccs2026@gmail.com} in advance if you have any AV concerns.
\end{itemize}

\subsection{Pre-Talk Checklist}
\begin{itemize}
    \item[$\square$] Stable internet connection confirmed
    \item[$\square$] Zoom desktop client installed and updated (not browser-only)
    \item[$\square$] Microphone and camera tested
    \item[$\square$] Slides ready to screen-share
    \item[$\square$] Joined the correct room and promoted to presenter by host
    \item[$\square$] Notified session chair of any special requirements
\end{itemize}

% ============================================================
\section{Technical Support}

If you experience technical difficulties during the conference:\\[0.3em]
\textbf{Email:} \href{mailto:nerccs2026@gmail.com}{nerccs2026@gmail.com}\\
\textbf{On-call Zoom host:} [PLACEHOLDER: name and contact method during conference hours]\\[0.3em]
\textit{Note: Have a backup copy of your slides (e.g., PDF) available in case of screen-share issues.}

% ============================================================
\section{Code of Conduct}

Remote participants are expected to follow the same professional standards as in-person attendees.\\
[PLACEHOLDER: Link to or summary of the conference code of conduct.]

\end{document}
